---
title: "Importing Datasets from Local System"
description: |
  How to import datasets from local repository or file..
author:
  - name: DACSS Tutor
    affiliation: University of Massachusetts, Amherst
    affiliation_url: https://www.umass.edu
    
    
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    code_folding: true

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

```


## What is Local system?

Any computing device with data storage ability is referred to as our Local system. It could be our laptops, desktops, tablets, touch phones, etc. 

### What is Local repository or file?

Any file that we create in our local computing device to store objects, documents, or datasets is referred to as local reposiorty or file.


## How to import dataset from Local system?

In the previous tutorial, we discussed importing datasets from Github. Now, we will discuss how easily we can import datasets from any file from our system without giving the complete `url` path in the function argument. 

The first thing that we need to do is to find out where our working directory rests. We can easily do so by using `getwd()` function. In the below code chunk, we will use the function to see where is the `DACSS Tutor` working directory currently. 



```{r Working Directory Check}

getwd()

```
From the output, we can observe that location of the working directory. Suppose, we need to set it elsewhere then we can do so by using the function `setwd()` function. For the purpose of this tutorial we will use the existing locating of the working directory.The below code chunk shows a hashed out function to set the working directory by using the complete url path for location where you want to set your working directory. 


```{r Setting Working Directory Location}

# setwd("F:/DACSS-601-SUMMER-2022-BLOGS")


```

Let us now import a dataset from the working directory. The existing working directory is in `F` drive of the local system in the local file/repository `DACSS-601-SUMMER-2022-BLOGS`. Within the local file is a sub file `datasets` from where we will import `organiceggpoultry` dataset. It is in `excel` file format. 


```{r Importing Datsset from Local System}

# invoking "readxl" package to import csv file
library(readxl)

# assigning data set to an object
egg <- read_excel("F:/DACSS-601-SUMMER-2022-BLOGS/datasets/Advanced_ Uncleaned datasets/organiceggpoultry.xlsx")

knitr::kable(head(egg))

```

We can observe here that the dataset has been imported from the local system to R Studio. Using the `head()` function we are able to observe the first few records of the dataset. Ofcourse this dataset is unclean and messy hence, we are unable to get a clean view of the data. We will tackle the challenge of cleaning messy data in future tutorials. In case you have any questions regarding this tutorial, then kindly address your questions to your teaching assistant or faculty.
